%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jordan Moak's Resume					 %
% Date: 10/22/2017						 %
% Type: Software QA						 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%!TEX TS-program = xelatex
\documentclass[]{moak-resume}

% Packages
\usepackage{afterpage}
\usepackage{hyperref}
\usepackage{color}
\usepackage{xcolor}
\usepackage{smartdiagram}
\usepackage{fontspec}
\usepackage{metalogo}
\usepackage{tikz}
\usetikzlibrary{mindmap,shadows}
\usepackage{pgf-pie}
\usepackage{pstricks}
\usepackage{fontawesome5}

% Light gray for subtle keywords
\definecolor{keywordgray}{RGB}{180,180,180}

% Document Meta information.
\hypersetup{
    pdftitle={Jordan Moak's Resume},
    pdfauthor={Jordan Moak},
    pdfsubject={Resume},
    pdfkeywords={The Best, Senior Software Engineer, Systems Architect, Platform Engineering, Java, TypeScript, Python, LLM Integration, MCP, Automation, CI/CD, Microservices},
    colorlinks=false,           % no link border color
    allbordercolors=white       % white border color for all
}

\begin{document}

% Visible keywords for LLM/ATS parsing (subtle gray)
\noindent\textcolor{keywordgray}{\small\textit{Keywords: Senior Software Engineer, 13+ years, platform engineering, system architecture, automation, $48K+ savings, AI/LLM, MCP, TypeScript, Java, Node.js}}

\makeprofile{Jordan}{Moak}
            {Senior Software Engineer}
            {\icon{\faPhone} +513 417 4499}
            {\icon{\faEnvelope[regular]} \href{mailto:jordan.moak@gmail.com}{ jordan.moak@gmail.com}}
            {\icon{\faGithub} \href{https://github.com/JMoak/}{ JMoak}}
            {\icon{\faLinkedin} \href{https://www.linkedin.com/in/jmoak/}{ /in/JMoak}}
            {\icon{\faMapMarker} \href{https://www.google.com/maps/place/Greendale,+IN+47025/@39.1487958,-84.7652822,12z/data=!4m6!3m5!1s0x8841d3fcc3d9708d:0x528857ad3dfc5551!8m2!3d39.1125572!4d-84.8641178!16zL20vMHNrdHk?entry=ttu}{ Greendale, IN}}

% In the aside, each new line forces a line break
\begin{aside}
  \profilesection{About Me}
  \small\bodyfont Systems architect with 13+ years of experience designing and shipping software across healthcare, marketplace, and platform engineering domains. I translate complex system designs into production infrastructure — from Java microservices to AI agent orchestration. Proven track record of delivering \$48K+ annual cost savings and reclaiming dozens of engineer-hours weekly through automation and architectural improvements.
  \profilesection{Programming}
	\programmingPie{}
  ~
  \profilesection{Technical Skills}
  \smartdiagram[bubble diagram]{
      \textbf{Platform Integration},
      \textbf{CI/CD},
      \textbf{Micro-Services},
      \textbf{Automation},
      \textbf{Java Ecosystem},
      \textbf{TypeScript/Node.js}
  }
  ~
  \profilesection{Emerging Tech}
  \small\bodyfont LLM Integration, MCP Protocol, AI Agent Architecture, LangGraph, Local LLM Deployment
\end{aside}
~
% \section{Summary}
% \begin{entrylist}
% 	\entry
% 	{}
% 	{}
% 	{}
% 	{Dedicated, enthusiastic, and passionate programmer with experience in testing automation and the statistical analysis associated with medical device QA and clinical trials.  Driven by the prospect of exceeding expectations in the confrontation of challenging projects and responsibilities which expand personal skills, knowledge, and problem-solving ability.  Ambitious indiviudal offering a combination of exceptional motivation and a great logical sense to ensure the completion of projects ahead of expected timelines.\\}
% \end{entrylist}
% \\
\section{Experience}

  % -- Care.com
  \begin{entrylist}
    \entry
    {[Oct 2021 - Present]}
    {Senior Software Engineer}
    {Care.com}
    {Promoted Feb 2024}
  \end{entrylist}
  \begin{itemize}
    \setlength\itemsep{-0.4em}
    \item \small\bodyfont Architected and delivered automation on critical monolith production deployment pipeline, reclaiming 1+ engineer-week per week and enabling safe, quality deployment of 10-70 commits twice weekly (up from bi-weekly releases of 140+ commits with no automation).
    \item \small\bodyfont Delivered \$48K+ annual cost savings via Apache to Akamai subset replatform completed in 2 weeks.
    \item \small\bodyfont Led integration of Backstage Service Catalog (Node.js) and SonarQube with associated CI/CD pipelines, establishing platform engineering standards adopted organization-wide.
    \item \small\bodyfont Serve as technical anchor for legacy platform knowledge with ownership in rehabbing critical platform features and CI/CD processes for 10-person senior engineering team.
    \item \small\bodyfont Drive architectural pattern improvements scaling across multiple teams with strategic bend toward new AI/LLM agentic tooling.
    \newline
  \end{itemize}  

 % -- ANGI
 \begin{entrylist}
  \entry
    {[Nov 2018 - Oct 2021]}
    {Software Engineer III}
    {Angi (formerly known as Angie's List)}
    {}
\end{entrylist}
\begin{itemize}
  \setlength\itemsep{-0.4em}
  \item \small\bodyfont Designed and implemented code-generation templates and developer tooling adopted by delivery teams across the organization.
  \item \small\bodyfont Architected RESTful microservice testing framework using Node.js, Mountebank, and Cucumber, enabling CI/CD support via CircleCI.
  \item \small\bodyfont Led development of Appium-based mobile testing framework supporting four mobile applications with Python, XCUITest, and UIAutomator2.
  \item \small\bodyfont Built and maintained Selenium-based frontend testing framework for microfrontend architecture.
  \item \small\bodyfont Evangelized automation best practices through documentation, bootcamps, and organizational support.
  \newline
\end{itemize}

 % -- ROCHE
\begin{entrylist}
  \entry
    {[Sep 2014 - Nov 2018]}
    {DV Software Engineer}
    {Roche Diagnostics (Contracted through PRO Unlimited)}
    {}
\end{entrylist}
\begin{itemize}
  \setlength\itemsep{-0.4em}
  \item \small\bodyfont Automated mobile-web-medical-device ecosystem using Java, Appium, Selenium, and Linux bash for FDA-compliant medical device validation.
  \item \small\bodyfont Created reusable automation tools using Java, Selenium, PowerShell, and SAS within regulated standard operating procedures.
  \item \small\bodyfont Led team automation of test dataset and configuration file generation for medical software verification.
  \newline
\end{itemize}

% -- TSC
\begin{entrylist}
  \entry
    {[Mar 2014 - Aug 2014]}
    {Programmer/Analyst}
    {The Stevenson Company}
    {}
\end{entrylist}
\begin{itemize}
  \setlength\itemsep{-0.4em}
  \item \small\bodyfont Developed statistical procedures for quality analysis and data cleaning in market research web applications.
  \item \small\bodyfont Migrated SAS programs to MySQL and PHP, improving processing efficiency and code maintainability.
  \newline
\end{itemize}

% -- STATKING
\begin{entrylist}
    \entry
    {[Jan 2013 - Dec 2013]}
    {Statistical Programmer}
    {STATKING Clinical Services}
    {}
  \end{entrylist}
\begin{itemize}
  \setlength\itemsep{-0.4em}
  \item \small\bodyfont Led programming for 20+ Phase I-III clinical trials, developing CDISC SDTM and ADaM datasets in SAS.
  \item \small\bodyfont Produced 160+ analysis tables and listings for Phase III clinical trial submission.
  \newline
\end{itemize}  

\section{Selected Personal Projects}
\begin{entrylist}
  \entry
    {[GitHub: JMoak]}
    {Published NPM Packages}
    {MCP Server Ecosystem}
    {}
\end{entrylist}
\begin{itemize}
  \setlength\itemsep{-0.4em}
  \item \small\bodyfont \textbf{chrono-mcp}: Production Model Context Protocol server for date/time operations. Dynamically-shaped, token-optimized responses. Published to NPM with 400+ IANA timezone support.
  \item \small\bodyfont \textbf{vibrissa}: JSON-driven MCP integration test runner. Declarative test cases over stdio, CI/CD ready with JUnit output.
  \item \small\bodyfont Applied protocol-based architecture and comprehensive documentation patterns (ARCHITECTURE.md, AGENTS.md) from platform engineering to developer tooling.
  \newline
\end{itemize}

\begin{entrylist}
  \entry
    {[GitHub: JMoak]}
    {AI Agent Architecture}
    {LangGraph Multi-Agent System}
    {}
\end{entrylist}
\begin{itemize}
  \setlength\itemsep{-0.4em}
  \item \small\bodyfont Built multi-workflow AI agent platform supporting plan-execute-validate, screenshot analysis, and game automation workflows.
  \item \small\bodyfont Architected unified LLM abstraction layer supporting LangChain, direct HTTP, and local LLM backends (LM Studio) with graceful stub fallbacks.
  \item \small\bodyfont Implemented protocol-based agent composition, source tracking for observability, and feature-flag safety controls.
  \newline
\end{itemize}

\section{Education}
\begin{entrylist}
  \entry
    {[2008 - 2013]}
    {Bachelor's Degree in Mathematics}
    {Northern Kentucky University}
    {Specialization in Applied Mathematics\\}
  \entry
    {[2008 - 2013]}
    {Bachelor's Degree in Statistics}
    {Northern Kentucky University}
    {Capstone: R-based anomaly detection for credit card fraud\\}
\end{entrylist}
\end{document}
